Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing

### 2018-04-29 paper.tex
lensing.py is now much more legitimate
Fixed an error in the NFW sigma formula, added Halo base class to reduce code repetition
Added pretty much complete analysis code
Data exported with correct uncertainty on the mean

\begin{document}
\title{Distinguishing NFW and Isothermal Density Profiles with Gravitational Lensing}
\author{}
\date{\today}
\maketitle

\begin{abstract}
We attempt to distinguish NFW and cored isothermal density profiles using weak gravitational lensing shear.
\end{abstract}

@@

\[\sigma^2 = \frac{G M_{200}}{2 \left(
    \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}}
    - r_c \arctan \left(
        \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit} {r_c}^3}
    \right)
\right)}\]
\[\sigma^2 = \frac{G M_{200}}{2 \left(
    \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}}
    - D_L \theta_c \arctan \left(
        \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit} {D_L}^3 {\theta_c}^3}
    \right)
\right)}\]

@@

\[M_{200} = M_{enc}(r_{200}) = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3\]
\[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]

@@

\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}} \right) \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right)\]
[Bartelmann 2001]

@@

\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \right) \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right)\]

@@

\[\delta_C = \frac{200}{3} \frac{C^3}{\ln(1 + C) - C/(1 + C)}\]

\[r_s = \frac{1}{C} \left(\frac{3M_{200}}{800\pi \rho_\mathrm{crit}}\right)^\frac{1}{3}\]

\[C = \frac{r_{200}}{r_s}\]

@@

>>>>

\begin{document}
\title{Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing}
\author{}
\date{\today}
\maketitle

\begin{abstract}
We examine the feasibility of distinguishing NFW and cored isothermal density profiles using weak gravitational lensing shear.
\end{abstract}

@@

\[\sigma^2 = \frac{M_{200} G}{2 \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)}\]

@@

\[M_{200} = 200 \rho_\mathrm{crit} \frac{4}{3} \pi {r_{200}}^3\]
\[M_{200} = M_\mathrm{enc}(r_{200}) = \frac{2 \sigma^2}{G} \left( r_{200} - r_c \arctan{\left(\frac{r_{200}}{r_c}\right)} \right)\]
\[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]

@@

\[\Sigma_\mathrm{NFW}(R) = \frac{2 \rho_\mathrm{crit} \delta_C r_s}{(R/r_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(R/r_s)^2 - 1}}  \arctan\left(\sqrt{\frac{R/r_s - 1}{R/r_s + 1}} \right) \right)\]
[Bartelmann 2001]

@@

\[\Sigma_\mathrm{NFW}(\theta) = \frac{2 \rho_\mathrm{crit} \delta_C D_L \theta_s}{(\theta/\theta_s)^2 - 1} \left(1 - \frac{2}{\sqrt{(\theta/\theta_s)^2 - 1}} \arctan\left(\sqrt{\frac{\theta/\theta_s - 1}{\theta/\theta_s + 1}} \right) \right)\]

@@

\[\delta_C = \frac{200}{3} \frac{C^3}{\ln(1 + C) - C/(1 + C)}\]
\[r_s = \frac{r_{200}}{C}\]
\[r_{200} = \left( \frac{3 M_{200}}{800 \pi \rho_\mathrm{crit}} \right)^{1/3}\]
\[C = \frac{r_{200}}{r_s}\]

@@

Assume same DS since this can be determined by redshift anyway

estimating ellipticity has well-documented issues [cite] due to noise and PSF
